---
title: "Prediction Assignment"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Proccessing

First the data are imported into R and formatted:

```{r echo=TRUE}
dat = read.csv("C:/Users/U410DA/Desktop/coursera/Practical Machine learning/pml-training.csv")
dat$classe<-as.factor(dat$classe)
dat[,7:159] <- sapply( dat[,7:159], as.numeric )


library(caret)

library(gbm)
```

## Splitting Dataset into Test/Train datasets

Since the dataset is rather large, only 1/4 of the data and only 6 predictors are used as the training data set. THe results later showed that this was sufficient to build a good model.

```{r  echo=TRUE}
set.seed(200)
inTrain = createDataPartition(dat$classe, p = 1/4)[[1]]


training = dat[ inTrain,c(6:11,160)]
testing = dat[-inTrain,]
```

## Fitting a model

A GBM model was constructed to predict the value of "classe"


```{r}
set.seed(200)

modelFit2<-train(classe~.,data=training,method="gbm",verbose=FALSE, na.action = na.pass)

```

## Results

Confusion Matrices show high accuracy on both the training and testing datasets:

```{r}

confusionMatrix(table(training$classe,predict(modelFit2,training) ))
confusionMatrix(table(testing$classe,predict(modelFit2,testing) ))


```





